Energy and the CES production function

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
permuting order of vertices in triPlot()

<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
                labels=c("alpha[e]", "alpha[k]", "alpha[l]"), size=2.0)
@

@@

<<fig.height=3>>=
triPlot(
  data=
    AllCoeffs %>% 
    mutate( Model = interaction(nest, CSP, sep = " -- ", drop=TRUE),
            Inputs = flavor), 
  aes(x = alpha_3, y = alpha_1, z = alpha_2, 
      fill  = Model, 
      shape = Model,
      size = Model, 
      color = Inputs),
  alpha = 0.6) +
  facet_grid(. ~ Country) +
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6)) +
  scale_shape_manual(values = 21:25)  
@

>>>>

<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
@

@@

<<fig.height=3>>=
triPlot(
  data=
    AllCoeffs %>% 
    mutate( Model = interaction(nest, CSP, sep = " -- ", drop=TRUE),
            Inputs = flavor), 
  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
      fill  = Model, 
      shape = Model,
      size = Model, 
      color = Inputs),
  alpha = 0.6) +
  facet_grid(. ~ Country) +
  scale_colour_manual(values = c("gray70", "black")) +
  scale_size_manual(values = c(5, 3,3,3,3)) +
  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6)) +
  scale_shape_manual(values = 21:25)  
@
